\textbf{NBA Party}

### 2017-05-09 init_model.rnw
Now saving mlb_bets.pdf

### 
betting.days <- lines[year(date) == 2016][idx, date]
running.prof <- cumsum(ifelse(is.na(b), 0, b))
plot(x = 1:length(b), y = running.prof, 
     main = 'Profits over the 2016 season', 
     xlab = 'Game Number', ylab = 'Profit', type = 'l')
abline(a = 0, b = 0, lty = 3)
points(x = which.min(running.prof), y = min(running.prof), type = 'p')
text(x = which.min(running.prof), y = min(running.prof), labels = min(running.prof), pos = 4)

>>>>

### 
pdf('mlb_bets.pdf')
betting.days <- lines[year(date) == 2016][idx, date]
running.prof <- cumsum(ifelse(is.na(b), 0, b))
plot(x = 1:length(b), y = running.prof, 
     main = 'Profits over the 2016 season', 
     xlab = 'Game Number', ylab = 'Profit', type = 'l')
abline(a = 0, b = 0, lty = 3)
points(x = which.min(running.prof), y = min(running.prof), type = 'p')
text(x = which.min(running.prof), y = min(running.prof), labels = min(running.prof), pos = 4)
dev.off()
